PODD Ontology Driven Database

### 2012-03-12 epncanberra2012/Podd-20120313.tex
more changes to canberra presentation
add example and demo, although the example is currently sited in the demo

\begin{itemize}
 \item PODD implemented between 2009 and 2011
 \item Design by Yuan Fang Li and Gavin Kennedy
\end{itemize}

@@

@@

@@

@@

\begin{enumerate}
 \item Current implementation does not scale
 \item Object oriented, pulling document into memory
\end{enumerate}

@@

>>>>

\begin{itemize}
 \item PODD implemented between 2009 and 2011
 \item Design by Yuan Fang Li and Gavin Kennedy for High Resolution Plant Phenomics Centre
\end{itemize}

@@

\begin{itemize}
 \item Flexible scientific experiment management
 \item Use RDF and OWL technology to support science
\end{itemize}

@@

Simultaneous Phenotyping of Drought Stress Tolerance in Arabidopsis OST1-2 Mutant and Wild Type

Credit to Xueqin Wang for the example design : \url{http://podd.plantphenomics.org.au/podd/object/poddObject:838}

@@

\url{http://podd.plantphenomics.org.au/podd}

@@

\begin{enumerate}
 \item Current implementation does not scale with experiment size
 \item Only supports OWL-1.1
 \item Uses old versions of Fedora and Spring
\end{enumerate}

@@

\begin{itemize}
 \item Use upcoming SPARQL 1.1 Query and Update standards
 \item Use OWL-2 and pure SPARQL access to databases
 \item Support links from experiments to other RDF documents
\end{itemize}
